---
title: "Analysis-For-Submission"
author: "Sarah Lotspeich"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

# Setup 

```{r, message = FALSE, warning = FALSE}
# Load packages
library(missALI) ## for models x missing data corrections 
library(pROC) ## for ROC curves and AUC 
library(ggplot2) ## for plots (in general)
library(patchwork) ## for multi-panel plots 
library(naniar) ## for upset plots of missing data patterns

# Read in data on hospitalizations (suppressed for privacy)
hosp_dat = read.csv("~/Documents/missALI_prediction/data/deidentified_ali_hospitalizations.csv")
```

# Exploratory Data Analysis {.tabset}

## Figure 2
##### Patterns of missingness in the $10$ allostatic load index (ALI) for the $n = 1000$ patients in the sample from the electronic health records (EHR) at Atrium Health Wake Forest Baptist Hospital. Each row represents one of the $18$ distinct missing data patterns, and within that row the ALI component(s) with an ``X'' were missing.

```{r, include = FALSE}
# 0. Define and name missing patterns 
ali_miss_pat = hosp_dat |> 
  mutate(across(A1C:BP_SYSTOLIC, 
                .fns = ~ if_else(is.na(.), 1, 0), 
                .names = "MISS_{.col}")) |> 
  group_by(across(starts_with("MISS"))) |> 
  summarize(n = n()) |> 
  arrange(desc(n)) |> 
  ungroup() |> 
  mutate(miss_pat = paste0("MP-", 1:n()))
# 1. Prepare data and add custom labels
annotated_data <- ali_miss_pat |>
  mutate(
    Pattern_Label = paste0("Pattern ", row_number(), "\n(", n, " Patients)"),
    Pattern_Label = reorder(Pattern_Label, row_number())
  ) |>
  pivot_longer(
    cols = starts_with("MISS_", ignore.case = FALSE), 
    names_to = "Variable", 
    values_to = "Missing"
  ) |>
  mutate(
    Variable = sub("MISS_", "", Variable),
    # Create an explicit text column: put an "X" if missing, leave blank if observed
    cross_label = ifelse(Missing == 1, "X", "")
  )

# 2. Plot the tile map with the text overlay
ggplot(annotated_data, aes(x = Variable, y = Pattern_Label)) +
  # The base grid layer
  geom_tile(aes(fill = factor(Missing)), color = "white", linewidth = 0.4) +
  
  # The text overlay layer: places the "X" right in the center of the tiles
  geom_text(aes(label = cross_label), color = "#f6cec3", size = 3.5, fontface = "bold") +
  
  # Color scale styling (using clean, modern muted tones)
  scale_fill_manual(
    values = c("0" = "#f0ede6", "1" = "#e76f51"), # Off-white for observed, light peach/red tint for missing
    labels = c("0" = "Observed", "1" = "Missing"), 
    name = ""
  ) +
  theme_minimal(base_size = 16) +
  scale_x_discrete(
    labels = function(x) {
      # 1. Map your raw dataframe strings to clean clinical names
      clean_names <- c(
        BP_SYSTOLIC  = "BP Systolic",
        BP_DIASTOLIC = "BP Diastolic",
        BMI          = "Body Mass Index",
        ALB          = "Serum Albumin",
        TRIG         = "Triglycerides",
        CHOL         = "Cholesterol",
        A1C          = "Hemoglobin A1C",
        HCST         = "Homocysteine",
        CRP          = "C-Reactive Protein",
        CREAT_C      = "Creatinine Clearance"
      )
      
      # 2. Look up the clean name, and wrap it at a width of 10 characters
      stringr::str_wrap(clean_names[x], width = 10)
    }
  ) +
  labs(
    x = "Allostatic Load Index Component", 
    y = "Missing Data Pattern (Number of Patients)"
  ) +
  theme(
    axis.title = element_text(face = "bold"),
    #axis.text.x = element_text(angle = 45, hjust = 1, color = "black"),
    axis.text.y = element_text(color = "black"),
    panel.grid = element_blank(),
    legend.title = element_blank(), 
    legend.position = "top"
  )
ggsave(filename = "~/Documents/missALI_prediction/figures/ali_miss_patterns.png", 
       device = "png", width = 13, height = 9, units = "in")
```

## Figure 3 
##### Distributions of the allostatic load index (ALI) for the $n = 1000$ patients in the sample from the electronic health records (EHR) at Atrium Health Wake Forest Baptist Hospital after using the complete-case proportion and best/worst case imputation missing data methods. 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
ali_box_dat = hosp_dat |> 
  select(PAT_MRN_ID, A1C:BP_SYSTOLIC) |> 
  tidyr::gather(key = "COMPONENT", value = "VALUE", -1) |> 
  group_by(PAT_MRN_ID) |> 
  summarize(CC_PROP_ALI = mean(VALUE, na.rm = TRUE), 
            BEST_CASE_ALI = sum(ifelse(is.na(VALUE), 0, VALUE), na.rm = TRUE) / 10, 
            WORST_CASE_ALI = sum(ifelse(is.na(VALUE), 1, VALUE), na.rm = TRUE) / 10, ) 
ali_box_dat |> 
  select(-PAT_MRN_ID) |> 
  summarize_all(median)
ali_boxplots = ali_box_dat |> 
  tidyr::gather(key = "MISS_METH", value = "VALUE", -1) |> 
  mutate(MISS_METH = factor(x = MISS_METH, 
                            levels = c("BEST_CASE_ALI",
                                       "CC_PROP_ALI", 
                                       "WORST_CASE_ALI"), 
                            labels = c("Best Case Imputation", 
                                       "Complete-Case Proportion", 
                                       "Worst Case Imputation"))) |> 
  ggplot(aes(x = MISS_METH, y = VALUE, fill = MISS_METH)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#218288", "#FF855D", "#c1dbd0"), guide = "none") + 
  scale_x_discrete(labels = scales::label_wrap(12)) +
  theme_minimal(base_size = 14) +
  labs(x = "Missing Data Technique",
       y = "Allostatic Load Index (ALI)") + 
  theme(axis.title = element_text(face = "bold"), 
        title = element_text(face = "bold")) + 
  coord_flip()
ali_boxplots
ggsave(
  filename = "~/Documents/missALI_prediction/figures/compare_ali_boxplot.png",
  plot = ali_boxplots,
  device = "png",
  width = 10,
  height = 7,
  units = "in"
)
```

## Figure 4
##### Proportion of $n = 1000$ patients in the sample from the electronic health records (EHR) at Atrium Health Wake Forest Baptist Hospital with healthy, unhealthy, and missing values across the $10$ allostatic load index (ALI) components, after discretizing the original numeric biomarkers at their clinically meaningful thresholds from Table 1.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Use exactly 3 colors (ordered to match factor levels below)
cols3 <- c(
  "Missing"   = "#218288",
  "Unhealthy" = "#FF855D",
  "Healthy"   = "#c1dbd0"
)

# Convert 0/1/NA into labeled factor
make_miss_factor <- function(x) {
  dplyr::case_when(
    is.na(x) ~ "Missing",
    x == 0   ~ "Healthy",
    x == 1   ~ "Unhealthy",
    TRUE     ~ NA_character_   # in case anything unexpected appears
  ) |>
    factor(levels = c("Missing", "Unhealthy", "Healthy"))
}

# Select components + recode
ali_components_only <- hosp_dat |>
  select(A1C:BP_SYSTOLIC) |>
  mutate(across(everything(), make_miss_factor))

# Pivot to long
long_ali <- ali_components_only |>
  pivot_longer(cols = everything(),
               names_to = "Component",
               values_to = "Value")

# Order components by MOST missing
order_levels <- long_ali |>
  group_by(Component) |>
  summarize(
    num_missing = sum(Value == "Missing"),
    .groups = "drop"
  ) |>
  arrange(desc(num_missing)) |>
  pull(Component)

# Plot
histogram_missing <- long_ali |>
  mutate(
    COMP = factor(Component, levels = order_levels),
    Finding = factor(Value, levels = c("Missing", "Unhealthy", "Healthy"))
  ) |>
  ggplot(aes(x = COMP, fill = Finding)) +
  geom_bar(position = "fill", color = "black", linewidth = 0.25) +
  scale_fill_manual(values = cols3, name = NULL) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(
  labels = c(
    BP_SYSTOLIC = "BP Systolic",
    BP_DIASTOLIC = "BP Diastolic",
    BMI = "Body Mass Index",
    ALB = "Serum Albumin",
    TRIG = "Triglycerides",
    CHOL = "Cholesterol",
    A1C = "Hemoglobin A1C",
    HCST = "Homocysteine",
    CRP = "C-Reactive Protein",
    CREAT_C = "Creatinine Clearance"
  )
)  +
  labs(
    x = "ALI Component",
    y = "Proportion of Measurements"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.title = element_text(face = "bold"),
    legend.position = "top",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  coord_flip()
histogram_missing
ggsave(
  filename = "~/Documents/missALI_prediction/figures/miss_healthy_unhealthy_barplot.png",
  plot = histogram_missing,
  device = "png",
  width = 10,
  height = 7,
  units = "in"
)
```

## Figure 5
##### Missingness upset plot displaying combinations of allostatic load index (ALI) components that were missing together for patients.

```{r, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
## Rename columns before making upset plot so that labels are readable
upset_plot = hosp_dat |> 
  rename(
    "Hemoglobin A1C" = A1C, 
    "Serum Albumin" = ALB,
    "Body Mass Index" = BMI,
    "Homocysteine" = HCST,
    "Systolic Blood Pressure" = BP_SYSTOLIC,
    "Diastolic Blood Pressure" = BP_DIASTOLIC,
    "Cholesterol" = CHOL,
    "C-Reactive Protein" = CRP,
    "Creatinine Clearance" = CREAT_C,
    "Triglycerides" = TRIG
  ) |> 
  select(-starts_with("NUM")) |> 
  gg_miss_upset(
    nsets = 10,
    sets.bar.color = "#218288",    
    main.bar.color = "#218288",
    matrix.color = "#218288")
png("~/Documents/missALI_prediction/figures/ali_components_upset.png", width = 800, height = 800, res = 150)
upset_plot
dev.off()
upset_plot
```

## Supplemental Figure S1
##### Distribution of number of hospitalizations in the $2$-year study period across n = 1000 patients.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
hosp_bar = hosp_dat |> 
  ggplot(aes(x = NUM_ADMIT)) + 
  geom_bar(fill = "#218288") + 
  theme_minimal(base_size = 14) +
  labs(x = "Count of Hospitalizations",
       y = "Count of Patients") + 
  theme(axis.title = element_text(face = "bold"), 
        title = element_text(face = "bold"))
hosp_bar
ggsave(
  filename = "~/Documents/missALI_prediction/figures/count_hosp_bar.png",
  plot = hosp_bar,
  device = "png",
  width = 10,
  height = 7,
  units = "in"
)
```

# Results {.tabset}

```{r, echo = FALSE}
# Helper function to make ggplot ROC curves from full-sample fits 
full_sample_roc = function(roc_obj, line_col, method_title) {
  ## Create label AUC = 0.XXX
  label_auc = paste0("= ", round(auc(roc_obj), 3), " (", 
                     round(ci.auc(roc_obj)[1], 3), ", ", 
                     round(ci.auc(roc_obj)[2], 3), ")")
  
  ## Make dataframe of ROC coordinates to plot
  #plot_roc_df = coords(roc_obj)
  
  ## Plot ROC curve(s) using ggplot2
  roc_obj |>
    ### Plot ROC coordinates
    ggroc(legacy.axes = TRUE, color = line_col) + 
    ### Add dashed line of equality for reference
    geom_abline(slope = 1,
                intercept = 0,
                linewidth = 0.5,
                linetype = "dashed") + 
    ### Final formatting
    theme_minimal(base_size = 14) +
    coord_equal() +
    annotate(geom = "text",
             x = 1,
             y = 0.07,
             hjust = 1,
             vjust = 0,
             label = "bold('AUC (95% CI)')", 
             parse = TRUE) +
    annotate(geom = "text",
             x = 1,
             y = 0,
             hjust = 1,
             vjust = 0,
             label = label_auc) +
    labs(x = "1 - Specificity",
         y = "Sensitivity", 
         title = method_title) + 
    theme(axis.title = element_text(face = "bold"), 
          title = element_text(face = "bold"))
}

# Define color scheme 
miss_meth_cols = c("#2b9d8f", "#e76f51", "#1b3c73", "#c1dbd0", 
                   "#a8c56e", "#6a4c93", "#e8b89a", "#c0404a")
```

```{r}
# Create empty dataframe to save AUC for all methods/models
save_auc = data.frame()
```

## Model 1: Logistic Regression {.tabset}
### Summary Measure Models {.tabset}
#### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 
##### Fit to Full Sample 

```{r}
# Logistic regression + complete-case proportion
mod_log_prop = cc_prop_approach(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial") 

# View the fitted model summary
mod_log_prop$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_prop = mod_log_prop$fit |> 
  predict(type = "response")

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_prop)
roc_log_prop = full_sample_roc(roc_obj = roc_curve, 
                               line_col = miss_meth_cols[1], 
                               method_title = "Complete-Case\nProportion")
roc_log_prop

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Complete-Case Proportion",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with complete-case proportion ALI
kfold_log_cc_prop = kfold_validate(outcome = "ANY_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "binomial", 
                                   miss_method = "cc_prop", 
                                   folds = 5)

## View AUC from 5 folds 
kfold_log_cc_prop$all_fold_auc
median(kfold_log_cc_prop$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_log_prop_k = kfold_log_cc_prop |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE,
            line_col = miss_meth_cols[1]) 
roc_log_prop_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Complete-Case Proportion", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_log_cc_prop$all_fold_auc)
    ))
```

#### Approach 2: Counts of Unhealthy and Missing Components 

##### Fit to Full Sample 

```{r}
# Logistic regression + count of missing / unhealthy
mod_log_num = num_miss_approach(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial") 

# View the fitted model summary
mod_log_num$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_num = mod_log_num$fit |> 
  predict(type = "response")

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_num)
roc_log_num = full_sample_roc(roc_obj = roc_curve, 
                              line_col = miss_meth_cols[2], 
                              method_title = "Counts of Unhealthy and\nMissing Components")
roc_log_num

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Counts of Unhealthy and Missing Components", 
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with complete-case proportion ALI
kfold_log_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "num_miss", 
                                    folds = 5)

## View AUC from 5 folds 
kfold_log_num_miss$all_fold_auc
median(kfold_log_num_miss$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_log_num_k = kfold_log_num_miss |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[2]) 
roc_log_num_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Counts of Unhealthy and Missing Components", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_log_num_miss$all_fold_auc)
    ))
```

#### Approach 3a: Best-Case Imputation

##### Fit to Full Sample 

```{r}
# Logistic regression + best-case imputation
mod_log_best = case_approach(outcome = "ANY_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             data = hosp_dat, 
                             family = "binomial", 
                             best = TRUE) 

# View the fitted model summary
mod_log_best$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_best = mod_log_best$fit |> 
  predict(type = "response")

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_best)
roc_log_best = full_sample_roc(roc_obj = roc_curve, 
                               line_col = miss_meth_cols[3], 
                               method_title = "Best Case\nImputation")
roc_log_best

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_best = kfold_validate(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial", 
                                miss_method = "best", 
                                folds = 5)

## View AUC from 5 folds 
kfold_log_best$all_fold_auc
median(kfold_log_best$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_log_best_k = kfold_log_best |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[3]) 
roc_log_best_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_log_best$all_fold_auc)
    ))
```

#### Approach 3b: Worst-Case Imputation

##### Fit to Full Sample 

```{r}
# Logistic regression + worst-case imputation
mod_log_worst = case_approach(outcome = "ANY_ADMIT", 
                              covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                              data = hosp_dat, 
                              family = "binomial", 
                              best = FALSE) 

# View the fitted model summary
mod_log_worst$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_worst = mod_log_worst$fit |> 
  predict(type = "response")

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_worst)
roc_log_worst = full_sample_roc(roc_obj = roc_curve, 
                                line_col = miss_meth_cols[4], 
                                method_title = "Worst Case\nImputation")
roc_log_worst

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with worst-case imputation
kfold_log_worst = kfold_validate(outcome = "ANY_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                 data = hosp_dat, 
                                 family = "binomial", 
                                 miss_method = "worst", 
                                 folds = 5)

## View AUC from 5 folds 
kfold_log_worst$all_fold_auc
median(kfold_log_worst$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_log_worst_k = kfold_log_worst |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[4]) 
roc_log_worst_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_log_worst$all_fold_auc)
    ))
```

#### ROC Curves for Approaches 1-3b 

The following plot displays the ROC curves for the four summary measure models side-by-side. 

```{r, echo = FALSE, fig.width = 14, fig.height = 8}
# comb_plot = (roc_log_prop | roc_log_prop_k) / 
#   (roc_log_num | roc_log_num_k) / 
#   (roc_log_best | roc_log_best_k) / 
#   (roc_log_worst | roc_log_worst_k) + 
comb_plot = (roc_log_prop | roc_log_num | roc_log_best | roc_log_worst) / 
  (roc_log_prop_k |  roc_log_num_k | roc_log_best_k | roc_log_worst_k) #+ 
  #plot_annotation(tag_levels = "A")
comb_plot
ggsave(filename = "~/Documents/missALI_prediction/figures/all_summ_meas_roc_log.png", 
       plot = comb_plot, 
       device = "png", width = 14, height = 8, units = "in")
```

### Separate Component Models {.tabset}

#### Approach 4a: Best-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# Logistic regression + best-case imputation (separate components)
mod_log_best = case_approach(outcome = "ANY_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             data = hosp_dat, 
                             family = "binomial", 
                             best = TRUE, 
                             comp_sep = TRUE) 

# View the fitted model summary
mod_log_best$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_best = mod_log_best$fit |> 
  predict(type = "response")

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_best)
roc_log_best = full_sample_roc(roc_obj = roc_curve, 
                               line_col = miss_meth_cols[5], 
                               method_title = "Best Case\nImputation")
roc_log_best

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_best_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "best", 
                                    comp_sep = TRUE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_log_best_sep$all_fold_auc
median(kfold_log_best_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_log_best_k = kfold_log_best_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[5]) 
roc_log_best_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_log_best_sep$all_fold_auc)
    ))
```

#### Approach 4b: Worst-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# Logistic regression + worst-case imputation (separate components)
mod_log_worst = case_approach(outcome = "ANY_ADMIT", 
                              covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                              data = hosp_dat, 
                              family = "binomial", 
                              best = FALSE, 
                              comp_sep = TRUE) 

# View the fitted model summary
mod_log_worst$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_worst = mod_log_worst$fit |> 
  predict(type = "response")

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_worst)
roc_log_worst = full_sample_roc(roc_obj = roc_curve, 
                                line_col = miss_meth_cols[6], 
                                method_title = "Worst Case\nImputation")
roc_log_worst

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_worst_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                     covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                     data = hosp_dat, 
                                     family = "binomial", 
                                     miss_method = "worst", 
                                     comp_sep = TRUE,
                                     folds = 5)

## View AUC from 5 folds 
kfold_log_worst_sep$all_fold_auc
median(kfold_log_worst_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_log_worst_k = kfold_log_worst_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[6]) 
roc_log_worst_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_log_worst_sep$all_fold_auc)
    ))
```

#### Approach 5: Missingness as a Category (Separate)

##### Fit to Full Sample

```{r}
# Logistic regression + missing as a category (separate components)
mod_log_cat = miss_cat_approach(outcome = "ANY_ADMIT",
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat,
                                family = "binomial")

# View the fitted model summary
mod_log_cat$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_cat = mod_log_cat$fit |> 
  predict(type = "response")

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_cat)
roc_log_cat = full_sample_roc(roc_obj = roc_curve, 
                              line_col = miss_meth_cols[7], 
                              method_title = "Missingness as\na Category")
roc_log_cat

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Missingness as a Category", 
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```


```{r, eval = FALSE}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_cat_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "binomial", 
                                   miss_method = "cat", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_log_worst_sep$all_fold_auc
median(kfold_log_worst_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_log_worst_k = kfold_log_worst_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[6]) 
roc_log_worst_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Missingness as a Category", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_log_worst_sep$all_fold_auc)
    ))
```

#### Approach 6: Pattern Submodels (Separate)

##### Fit to Full Sample

```{r}
# Logistic regression + pattern submodels (separate components)
## Define a mapping vector: index is the small row number, value is the parent row number
# parent_mapping = c(
#   "9" = 1, "10" = 1, "11" = 2, "12" = 2, "13" = 3, 
#   "14" = 5, "15" = 4, "16" = 4, "17" = 2, "18" = 3
# )
mod_log_patsub = pattern_submod_approach(outcome = "ANY_ADMIT",
                                         covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                         data = hosp_dat,
                                         family = "binomial")

# Calculate predicted probabilities
pred_prob_log_patsub = mod_log_patsub |> 
  predict_pattern_submod()

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_patsub)
roc_log_submod = full_sample_roc(roc_obj = roc_curve, 
                                 line_col = miss_meth_cols[8], 
                                 method_title = "Pattern\nSubmodels")
roc_log_submod

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Pattern Submodels", 
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_submod_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                      covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                      data = hosp_dat, 
                                      family = "binomial", 
                                      miss_method = "patsub", 
                                      comp_sep = TRUE,
                                      folds = 5)

## View AUC from 5 folds 
kfold_log_submod_sep$all_fold_auc
median(kfold_log_submod_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_log_submod_k = kfold_log_submod_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[8]) 
roc_log_submod_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Logistic", 
      Missing = "Pattern Submodels", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_log_submod_sep$all_fold_auc)
    ))
```

#### ROC Curves for Approaches 4a-6 

The following plot displays the ROC curves for the three separate component models side-by-side. 

```{r, echo = FALSE, fig.width = 9, fig.height = 9}
# comb_plot = (roc_log_best | roc_log_worst | roc_log_cat) / 
#   (roc_log_best_k | roc_log_worst_k | plot_spacer()) + 
#   plot_layout(heights = c(1, 1), widths = c(1, 1, 1))
design <- "
ABCD
EF#G
"
comb_plot <- (roc_log_best + roc_log_worst + roc_log_cat + roc_log_submod +
              roc_log_best_k + roc_log_worst_k + roc_log_submod_k) +
  plot_layout(design = design)
comb_plot
ggsave(filename = "~/Documents/missALI_prediction/figures/all_sep_comp_roc_log.png", 
       plot = comb_plot, 
       device = "png", width = 14, height = 8, units = "in")
```

## Model 2: Random Forest {.tabset}
### Summary Measure Models {.tabset}
#### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 
##### Fit to Full Sample 

```{r}
# Random forest + complete-case proportion
mod_rf_prop = cc_prop_approach(outcome = "ANY_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                               data = hosp_dat, 
                               family = "binomial", 
                               use_glm = FALSE) 

# View the fitted model summary
mod_rf_prop$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_prop = mod_rf_prop$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_prop)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Complete-Case Proportion",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

```{r, include = FALSE}
# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_rf_prop = full_sample_roc(roc_obj = roc_curve, 
                              line_col = miss_meth_cols[1], 
                              method_title = "Complete-Case\nProportion")
roc_rf_prop
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with complete-case proportion ALI
kfold_rf_cc_prop = kfold_validate(outcome = "ANY_ADMIT", 
                                  covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                  data = hosp_dat, 
                                  family = "binomial", 
                                  miss_method = "cc_prop", 
                                  use_glm = FALSE,
                                  folds = 5)

## View AUC from 5 folds 
kfold_rf_cc_prop$all_fold_auc
median(kfold_rf_cc_prop$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Complete-Case Proportion", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_rf_cc_prop$all_fold_auc)
    ))
```

```{r, include = FALSE}
## Plot individual ROC curves from 5 folds with median over top 
roc_rf_prop_k = kfold_rf_cc_prop |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE,
            line_col = miss_meth_cols[1]) 
```

#### Approach 2: Counts of Unhealthy and Missing Components 

##### Fit to Full Sample 

```{r}
# Logistic regression + count of missing / unhealthy
mod_rf_num = num_miss_approach(outcome = "ANY_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                               data = hosp_dat, 
                               family = "binomial", 
                               use_glm = FALSE) 

# View the fitted model summary
mod_rf_num$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_num = mod_rf_num$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_num)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Counts of Unhealthy and Missing Components",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with complete-case proportion ALI
kfold_log_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "num_miss", 
                                    folds = 5)

## View AUC from 5 folds 
kfold_log_num_miss$all_fold_auc
median(kfold_log_num_miss$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Counts of Unhealthy and Missing Components", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_log_num_miss$all_fold_auc)
    ))
```

#### Approach 3a: Best-Case Imputation

##### Fit to Full Sample 

```{r}
# Logistic regression + best-case imputation
mod_rf_best = case_approach(outcome = "ANY_ADMIT", 
                            covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                            data = hosp_dat, 
                            family = "binomial", 
                            best = TRUE, 
                            use_glm = FALSE) 

# View the fitted model summary
mod_rf_best$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_best = mod_rf_best$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_best)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Best Case Imputation",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with best-case imputation
kfold_rf_best = kfold_validate(outcome = "ANY_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                               data = hosp_dat, 
                               family = "binomial", 
                               miss_method = "best", 
                               use_glm = FALSE,
                               folds = 5)

## View AUC from 5 folds 
kfold_rf_best$all_fold_auc
median(kfold_rf_best$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_rf_best$all_fold_auc)
    ))
```

#### Approach 3b: Worst-Case Imputation

##### Fit to Full Sample 

```{r}
# Logistic regression + worst-case imputation
mod_rf_worst = case_approach(outcome = "ANY_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             data = hosp_dat, 
                             family = "binomial", 
                             best = FALSE, 
                             use_glm = FALSE) 

# View the fitted model summary
mod_rf_worst$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_worst = mod_rf_worst$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_worst)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Worst Case Imputation",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with worst-case imputation
kfold_rf_worst = kfold_validate(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial", 
                                miss_method = "worst", 
                                use_glm = FALSE,
                                folds = 5)

## View AUC from 5 folds 
kfold_rf_worst$all_fold_auc
median(kfold_rf_worst$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_rf_worst$all_fold_auc)
    ))
```

### Separate Component Models {.tabset}

#### Approach 4a: Best-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# Logistic regression + best-case imputation (separate components)
mod_rf_best_sep = case_approach(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial", 
                                best = TRUE, 
                                comp_sep = TRUE, 
                                use_glm = FALSE) 

# View the fitted model summary
mod_rf_best_sep$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_best_sep = mod_rf_best_sep$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_best_sep)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Best Case Imputation",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with best-case imputation
kfold_rf_best_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "binomial", 
                                   miss_method = "best", 
                                   comp_sep = TRUE,
                                   use_glm = FALSE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_rf_best_sep$all_fold_auc
median(kfold_rf_best_sep$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_rf_best_sep$all_fold_auc)
    ))
```

#### Approach 4b: Worst-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# Random forest + worst-case imputation (separate components)
mod_rf_worst_sep = case_approach(outcome = "ANY_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                 data = hosp_dat, 
                                 family = "binomial", 
                                 best = FALSE, 
                                 comp_sep = TRUE,
                                 use_glm = FALSE) 

# View the fitted model summary
mod_rf_worst_sep$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_worst_sep = mod_rf_worst_sep$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_worst_sep)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Worst Case Imputation",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with worst-case imputation
kfold_rf_worst_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "worst", 
                                    use_glm = FALSE,
                                    comp_sep = TRUE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_rf_worst_sep$all_fold_auc
median(kfold_rf_worst_sep$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_rf_worst_sep$all_fold_auc)
    ))
```

#### Approach 5: Missingness as a Category (Separate)

##### Fit to Full Sample 

```{r}
# Logistic regression + missing as a category (separate components)
mod_rf_cat = miss_cat_approach(outcome = "ANY_ADMIT",
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat,
                               family = "binomial", 
                               use_glm = FALSE)

# View the fitted model summary
mod_rf_cat$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_cat = mod_rf_cat$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_cat)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Missingness as a Category",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```


#### Approach 6: Pattern Submodels (Separate)

##### Fit to Full Sample

```{r}
# Random forest + pattern submodels (separate components)
mod_rf_patsub = pattern_submod_approach(outcome = "ANY_ADMIT",
                                        covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                        data = hosp_dat,
                                        family = "binomial", 
                                        use_glm = FALSE)

# Calculate predicted probabilities
pred_prob_rf_patsub = mod_rf_patsub |> 
  predict_pattern_submod()

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_patsub)
roc_rf_submod = full_sample_roc(roc_obj = roc_curve, 
                                 line_col = miss_meth_cols[8], 
                                 method_title = "Pattern\nSubmodels")
roc_rf_submod

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Pattern Submodels", 
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with pattern submodels
kfold_rf_submod_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "patsub", 
                                    comp_sep = TRUE,
                                    use_glm = FALSE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_rf_submod_sep$all_fold_auc
median(kfold_rf_submod_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_rf_submod_k = kfold_rf_submod_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[8]) 
roc_rf_submod_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Random Forest", 
      Missing = "Pattern Submodels", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_rf_submod_sep$all_fold_auc)
    ))
```

## Model 3: Poisson Regression {.tabset}
### Summary Measure Models {.tabset}
#### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 

##### Fit to Full Sample 

```{r}
#  poisson + complete-case proportion
mod_pois_prop = cc_prop_approach(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "poisson") 

# View the fitted model summary
mod_pois_prop$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_prop = mod_pois_prop$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_prop)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Complete-Case Proportion",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```
```{r, include = FALSE}
# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_pois_prop = full_sample_roc(roc_obj = roc_curve, 
                              line_col = miss_meth_cols[1], 
                              method_title = "Complete-Case\nProportion")
roc_pois_prop
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  poisson model with complete-case proportion ALI
kfold_pois_cc_prop = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "cc_prop", 
                                   folds = 5)

## View AUC from 5 folds 
kfold_pois_cc_prop$all_fold_auc
median(kfold_pois_cc_prop$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Complete-Case Proportion", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_pois_cc_prop$all_fold_auc)
    ))
```

```{r, include = FALSE}
## Plot individual ROC curves from 5 folds with median over top 
roc_pois_prop_k = kfold_pois_cc_prop |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE,
            line_col = miss_meth_cols[1]) 
```

#### Approach 2: Counts of Unhealthy and Missing Components 

##### Fit to Full Sample 

```{r}
# poisson regression + count of missing / unhealthy
mod_pois_num = num_miss_approach(outcome = "NUM_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat, 
                               family = "poisson")

# View the fitted model summary
mod_pois_num$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_num = mod_pois_num$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_num)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Counts of Unhealthy and Missing Components",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the poisson with complete-case proportion ALI
kfold_pois_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                    data = hosp_dat, 
                                    family = "poisson", 
                                    miss_method = "num_miss", 
                                    folds = 5)

## View AUC from 5 folds 
kfold_pois_num_miss$all_fold_auc
median(kfold_pois_num_miss$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Counts of Unhealthy and Missing Components", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_pois_num_miss$all_fold_auc)
    ))
```

#### Approach 3a: Best-Case Imputation

##### Fit to Full Sample 

```{r}
# poisson regression + best-case imputation
mod_pois_best = case_approach(outcome = "NUM_ADMIT", 
                            covar = c("SEX", "AGE_AT_ENCOUNTER"),
                            data = hosp_dat, 
                            family = "poisson", 
                            best = TRUE) 

# View the fitted model summary
mod_pois_best$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_best = mod_pois_best$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_best)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Best Case Imputation",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  poisson with best-case imputation
kfold_pois_best = kfold_validate(outcome = "NUM_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat, 
                               family = "poisson", 
                               miss_method = "best", 
                              folds = 5)

## View AUC from 5 folds 
kfold_pois_best$all_fold_auc
median(kfold_pois_best$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_pois_best$all_fold_auc)
    ))
```

#### Approach 3b: Worst-Case Imputation

##### Fit to Full Sample 

```{r}
# poisson regression + worst-case imputation
mod_pois_worst = case_approach(outcome = "NUM_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             data = hosp_dat, 
                             family = "poisson", 
                             best = FALSE) 

# View the fitted model summary
mod_pois_worst$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_worst = mod_pois_worst$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_worst)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Worst Case Imputation",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the poisson with worst-case imputation
kfold_pois_worst = kfold_validate(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson", 
                                miss_method = "worst", 
                                folds = 5)

## View AUC from 5 folds 
kfold_pois_worst$all_fold_auc
median(kfold_pois_worst$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_pois_worst$all_fold_auc)
    ))
```





### Separate Component Models {.tabset}

#### Approach 4a: Best-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# poisson regression + best-case imputation (separate components)
mod_pois_best_sep = case_approach(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson", 
                                best = TRUE, 
                                comp_sep = TRUE) 

# View the fitted model summary
mod_pois_best_sep$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_best_sep = mod_pois_best_sep$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_best_sep)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Best Case Imputation",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the poisson with best-case imputation
kfold_pois_best_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "best", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_pois_best_sep$all_fold_auc
median(kfold_pois_best_sep$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_pois_best_sep$all_fold_auc)
    ))
```

#### Approach 4b: Worst-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# poisson + worst-case imputation (separate components)
mod_pois_worst_sep = case_approach(outcome = "NUM_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                 data = hosp_dat, 
                                 family = "poisson", 
                                 best = FALSE, 
                                 comp_sep = TRUE) 

# View the fitted model summary
mod_pois_worst_sep$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_worst_sep = mod_pois_worst_sep$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_worst_sep)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Worst Case Imputation",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the poisson with worst-case imputation
kfold_pois_worst_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "poisson", 
                                    miss_method = "worst",
                                    comp_sep = TRUE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_pois_worst_sep$all_fold_auc
median(kfold_pois_worst_sep$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_pois_worst_sep$all_fold_auc)
    ))
```

#### Approach 5: Missingness as a Category (Separate)

```{r}
# poisson + missing as a category (separate components)
mod_pois_cat = miss_cat_approach(outcome = "NUM_ADMIT",
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat,
                               family = "poisson")

# View the fitted model summary
mod_pois_cat$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_cat = mod_pois_cat$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_cat)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Missingness as a Category",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```


#### Approach 6: Pattern Submodels (Separate)

##### Fit to Full Sample

```{r}
# Poisson + pattern submodels (separate components)
mod_pois_patsub = pattern_submod_approach(outcome = "NUM_ADMIT",
                                          covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                          data = hosp_dat,
                                          family = "poisson")

# Calculate predicted probabilities
pred_prob_pois_patsub = mod_pois_patsub |> 
  predict_pattern_submod()

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_patsub)
roc_pois_submod = full_sample_roc(roc_obj = roc_curve, 
                                  line_col = miss_meth_cols[8], 
                                  method_title = "Pattern\nSubmodels")
roc_pois_submod

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Pattern Submodels", 
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with pattern submodels
kfold_pois_submod_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                       covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                       data = hosp_dat, 
                                       family = "poisson", 
                                       miss_method = "patsub", 
                                       comp_sep = TRUE,
                                       folds = 5)

## View AUC from 5 folds 
kfold_pois_submod_sep$all_fold_auc
median(kfold_pois_submod_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_pois_submod_k = kfold_pois_submod_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[8]) 
roc_pois_submod_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Poisson", 
      Missing = "Pattern Submodels", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_pois_submod_sep$all_fold_auc)
    ))
```

## Model 4: Zero-Inflated Poisson Regression {.tabset}
### Summary Measure Models {.tabset}
#### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 

##### Fit to Full Sample 

```{r}
#  ZIP + complete-case proportion
mod_zip_prop = cc_prop_approach(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson") 

# View the fitted model summary
mod_zip_prop$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_prop = mod_zip_prop$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_prop)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Complete-Case Proportion",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

```{r, include = FALSE}
# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_zip_prop = full_sample_roc(roc_obj = roc_curve, 
                               line_col = miss_meth_cols[1], 
                               method_title = "Complete-Case\nProportion")
roc_zip_prop
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  ZIP model with complete-case proportion ALI
kfold_zip_cc_prop = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "cc_prop", 
                                   folds = 5)

## View AUC from 5 folds 
kfold_zip_cc_prop$all_fold_auc
median(kfold_zip_cc_prop$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Complete-Case Proportion", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_zip_cc_prop$all_fold_auc)
    ))
```

```{r, include = FALSE}
## Plot individual ROC curves from 5 folds with median over top 
roc_zip_prop_k = kfold_zip_cc_prop |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE,
            line_col = miss_meth_cols[1]) 
```

#### Approach 2: Counts of Unhealthy and Missing Components 

##### Fit to Full Sample 

```{r}
# ZIP regression + count of missing / unhealthy
mod_zip_num = num_miss_approach(outcome = "NUM_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                               zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat, 
                               family = "poisson")

# View the fitted model summary
mod_zip_num$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_num = mod_zip_num$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_num)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Counts of Unhealthy and Missing Components",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  ZIP with complete-case proportion ALI
kfold_zip_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                    zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                    data = hosp_dat, 
                                    family = "poisson", 
                                    miss_method = "num_miss", 
                                    folds = 5)

## View AUC from 5 folds 
kfold_zip_num_miss$all_fold_auc
median(kfold_zip_num_miss$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Counts of Unhealthy and Missing Components", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_zip_num_miss$all_fold_auc)
    ))
```

#### Approach 3a: Best-Case Imputation

##### Fit to Full Sample 

```{r}
# ZIP regression + best-case imputation
mod_zip_best = case_approach(outcome = "NUM_ADMIT", 
                            covar = c("SEX", "AGE_AT_ENCOUNTER"),
                            zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                            data = hosp_dat, 
                            family = "poisson", 
                            best = TRUE) 

# View the fitted model summary
mod_zip_best$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_best = mod_zip_best$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_best)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Best Case Imputation",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  ZIP with best-case imputation
kfold_zip_best = kfold_validate(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson", 
                                miss_method = "best", 
                                folds = 5)

## View AUC from 5 folds 
kfold_zip_best$all_fold_auc
median(kfold_zip_best$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_zip_best$all_fold_auc)
    ))
```

#### Approach 3b: Worst-Case Imputation

##### Fit to Full Sample 

```{r}
# ZIP regression + worst-case imputation
mod_zip_worst = case_approach(outcome = "NUM_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                             data = hosp_dat, 
                             family = "poisson", 
                             best = FALSE) 

# View the fitted model summary
mod_zip_worst$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_worst = mod_zip_worst$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_worst)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Worst Case Imputation",
      Separate_Components = "Summary Measure",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the ZIP with worst-case imputation
kfold_zip_worst = kfold_validate(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson", 
                                miss_method = "worst", 
                                folds = 5)

## View AUC from 5 folds 
kfold_zip_worst$all_fold_auc
median(kfold_zip_worst$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Summary Measure",
      Fit = "K-Fold", 
      AUC = median(kfold_zip_worst$all_fold_auc)
    ))
```

### Separate Component Models {.tabset}

#### Approach 4a: Best-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# ZIP regression + best-case imputation (separate components)
mod_zip_best_sep = case_approach(outcome = "NUM_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                 zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                 data = hosp_dat, 
                                 family = "poisson", 
                                 best = TRUE, 
                                 comp_sep = TRUE) 

# View the fitted model summary
mod_zip_best_sep$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_best_sep = mod_zip_best_sep$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_best_sep)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Best Case Imputation",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the ZIP with best-case imputation
kfold_zip_best_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "best", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_zip_best_sep$all_fold_auc
median(kfold_zip_best_sep$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Best Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_zip_best_sep$all_fold_auc)
    ))
```

#### Approach 4b: Worst-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# ZIP + worst-case imputation (separate components)
mod_zip_worst_sep = case_approach(outcome = "NUM_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                 zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                 data = hosp_dat, 
                                 family = "poisson", 
                                 best = FALSE, 
                                 comp_sep = TRUE) 

# View the fitted model summary
mod_zip_worst_sep$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_worst_sep = mod_zip_worst_sep$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_worst_sep)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Worst Case Imputation",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the ZIP with worst-case imputation
kfold_zip_worst_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                    data = hosp_dat, 
                                    family = "poisson", 
                                    miss_method = "worst",
                                    comp_sep = TRUE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_zip_worst_sep$all_fold_auc
median(kfold_zip_worst_sep$all_fold_auc) ### summarized by median

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Worst Case Imputation", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_zip_worst_sep$all_fold_auc)
    ))
```

#### Approach 5: Missingness as a Category (Separate)

```{r}
# ZIP + missing as a category (separate components)
mod_zip_cat = miss_cat_approach(outcome = "NUM_ADMIT",
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat,
                                family = "poisson")

# View the fitted model summary
mod_zip_cat$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_cat = mod_zip_cat$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_cat)

# Calculate AUC (95% Confidence Interval)
paste0(round(auc(roc_curve), 3), 
       " (", round(ci.auc(roc_curve)[1], 3), ", ", 
       round(ci.auc(roc_curve)[2], 3), ")")

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Missingness as a Category",
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

#### Approach 6: Pattern Submodels (Separate)

##### Fit to Full Sample

```{r}
# ZIP + pattern submodels (separate components)
mod_zip_patsub = pattern_submod_approach(
  outcome = "NUM_ADMIT",
  covar = c("SEX", "AGE_AT_ENCOUNTER"),
  zeros = c("SEX", "AGE_AT_ENCOUNTER"),
  data = hosp_dat,
  family = "poisson"
  )

# Calculate predicted probabilities
pred_prob_zip_patsub = mod_zip_patsub |> 
  predict_pattern_submod()

# Make the ROC curve 
## Include AUC (95% Confidence Interval)
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_patsub)
roc_zip_submod = full_sample_roc(
  roc_obj = roc_curve, 
  line_col = miss_meth_cols[8], 
  method_title = "Pattern\nSubmodels"
  )
roc_zip_submod

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Pattern Submodels", 
      Separate_Components = "Separate Components",
      Fit = "Full-Sample", 
      AUC = auc(roc_curve)
    ))
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the ZIP with pattern submodels
kfold_zip_submod_sep = kfold_validate(
  outcome = "NUM_ADMIT", 
  covar = c("SEX", "AGE_AT_ENCOUNTER"), 
  zeros = c("SEX", "AGE_AT_ENCOUNTER"), 
  data = hosp_dat, 
  family = "poisson", 
  miss_method = "patsub", 
  comp_sep = TRUE,
  folds = 5
  )

## View AUC from 5 folds 
kfold_zip_submod_sep$all_fold_auc
median(kfold_zip_submod_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
roc_zip_submod_k = kfold_zip_submod_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            line_col = miss_meth_cols[8]) 
roc_zip_submod_k

# Save AUC to dataframe 
save_auc = save_auc |> 
  rbind(
    data.frame(
      Model = "Zero-Inflated Poisson", 
      Missing = "Pattern Submodels", 
      Separate_Components = "Separate Components",
      Fit = "K-Fold", 
      AUC = median(kfold_zip_submod_sep$all_fold_auc)
    ))
```

# Barbell Plot: All Models and Methods 

```{r, echo = FALSE, message = FALSE, cache = FALSE}
save_auc |> 
  write.csv("~/Documents/missALI_prediction/data/forest_plot_data.csv", 
            row.names = FALSE)

barbell_data = save_auc |>
  dplyr::group_by(Missing, Fit, Separate_Components) |> 
  dplyr::summarize(barbell_lb = min(AUC), 
                   barbell_ub = max(AUC)) |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    Separate_Components = factor(x = Separate_Components,
                                 levels = c("Summary Measure", 
                                            "Separate Components"))
  ) 

barbell_plot = save_auc |> 
  dplyr::mutate(
    Separate_Components = factor(x = Separate_Components,
                                 levels = c("Summary Measure", 
                                            "Separate Components"))
  ) |> 
  ggplot() + 
  geom_linerange(data = barbell_data,
                 aes(x = Missing, ymin = barbell_lb, ymax = barbell_ub,
                     group = Fit),
                 position = position_dodge(0.5),
                 color = "#8c7b6b",
                 linewidth = 4.5,
                 alpha = 0.5) + 
  geom_point(aes(x = Missing, y = AUC, color = Model, 
             shape = Fit, group = Fit), position = position_dodge(0.5), size = 5) + 
  facet_grid(rows = vars(Separate_Components), scales = "free") + 
  scale_x_discrete(labels = scales::label_wrap(10)) +
  labs(x = "Missing Data Method", y = "AUC") + 
  coord_flip() + 
  scale_color_manual(values = miss_meth_cols) + 
  theme_minimal(base_size = 14) + 
  theme(axis.title = element_text(face = "bold"),
        legend.title = element_text(face = "bold"),
        legend.box.margin = margin(0, 0, 0, -75), 
        legend.position = "top", 
        strip.background = element_rect(fill = "black"), 
        strip.text = element_text(face = "bold", color = "white"), 
        panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  ggh4x::force_panelsizes(rows = c(1.33, 1)) #, respect = TRUE) 
barbell_plot
ggsave(filename = "~/Documents/missALI_prediction/figures/barbell_plot.png", 
       plot = barbell_plot, 
       device = "png", width = 10, height = 9, units = "in")
```
