---
title: "Analysis-For-Submission"
author: "Sarah Lotspeich"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Setup 

```{r}
# Load packages
library(missALI) ## for models x missing data corrections 
library(pROC) ## for ROC curves and AUC 

# Read in data on hospitalizations (suppressed for privacy)
hosp_dat = read.csv("~/Documents/missALI_prediction/data/deidentified_ali_hospitalizations.csv")
```

# Results {.tabset}

## Model 1: Logistic Regression {.tabset}
### Summary Measure Models {.tabset}
#### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 

##### Fit to Full Sample 

```{r}
# Logistic regression + complete-case proportion
mod_log_prop = cc_prop_approach(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial") 

# View the fitted model summary
mod_log_prop$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_prop = mod_log_prop$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_prop)
plot(roc_curve, 
     col = "#CD0BBC", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with complete-case proportion ALI
kfold_log_cc_prop = kfold_validate(outcome = "ANY_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "binomial", 
                                   miss_method = "cc_prop", 
                                   folds = 5)

## View AUC from 5 folds 
kfold_log_cc_prop$all_fold_auc
median(kfold_log_cc_prop$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_cc_prop |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 2: Counts of Unhealthy and Missing Components 

##### Fit to Full Sample 

```{r}
# Logistic regression + count of missing / unhealthy
mod_log_num = num_miss_approach(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial") 

# View the fitted model summary
mod_log_num$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_num = mod_log_num$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_num)
plot(roc_curve, 
     col = "#CD0BBC", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with complete-case proportion ALI
kfold_log_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "num_miss", 
                                    folds = 5)

## View AUC from 5 folds 
kfold_log_num_miss$all_fold_auc
median(kfold_log_num_miss$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_num_miss |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 3a: Best-Case Imputation

##### Fit to Full Sample 

```{r}
# Logistic regression + best-case imputation
mod_log_best = case_approach(outcome = "ANY_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             data = hosp_dat, 
                             family = "binomial", 
                             best = TRUE) 

# View the fitted model summary
mod_log_best$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_best = mod_log_best$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_best)
plot(roc_curve, 
     col = "#CD0BBC", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_best = kfold_validate(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial", 
                                miss_method = "best", 
                                folds = 5)

## View AUC from 5 folds 
kfold_log_best$all_fold_auc
median(kfold_log_best$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_best |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 3b: Worst-Case Imputation

##### Fit to Full Sample 

```{r}
# Logistic regression + worst-case imputation
mod_log_worst = case_approach(outcome = "ANY_ADMIT", 
                              covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                              data = hosp_dat, 
                              family = "binomial", 
                              best = FALSE) 

# View the fitted model summary
mod_log_worst$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_worst = mod_log_worst$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_worst)
plot(roc_curve, 
     col = "#CD0BBC", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with worst-case imputation
kfold_log_worst = kfold_validate(outcome = "ANY_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                 data = hosp_dat, 
                                 family = "binomial", 
                                 miss_method = "worst", 
                                 folds = 5)

## View AUC from 5 folds 
kfold_log_worst$all_fold_auc
median(kfold_log_worst$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_worst |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

### Separate Component Models {.tabset}

#### Approach 4a: Best-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# Logistic regression + best-case imputation (separate components)
mod_log_best = case_approach(outcome = "ANY_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             data = hosp_dat, 
                             family = "binomial", 
                             best = TRUE, 
                             comp_sep = TRUE) 

# View the fitted model summary
mod_log_best$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_best = mod_log_best$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_best)
plot(roc_curve, 
     col = "#CD0BBC", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_best_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "best", 
                                    comp_sep = TRUE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_log_best_sep$all_fold_auc
median(kfold_log_best_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_best_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 4b: Worst-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# Logistic regression + worst-case imputation (separate components)
mod_log_worst = case_approach(outcome = "ANY_ADMIT", 
                              covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                              data = hosp_dat, 
                              family = "binomial", 
                              best = FALSE, 
                              comp_sep = TRUE) 

# View the fitted model summary
mod_log_worst$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_worst = mod_log_worst$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_worst)
plot(roc_curve, 
     col = "#CD0BBC", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_worst_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                     covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                     data = hosp_dat, 
                                     family = "binomial", 
                                     miss_method = "worst", 
                                     comp_sep = TRUE,
                                     folds = 5)

## View AUC from 5 folds 
kfold_log_worst_sep$all_fold_auc
median(kfold_log_worst_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_worst_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 5: Missingness as a Category (Separate)

```{r}
# Logistic regression + missing as a category (separate components)
mod_log_cat = miss_cat_approach(outcome = "ANY_ADMIT",
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat,
                                family = "binomial")

# View the fitted model summary
mod_log_cat$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_log_cat = mod_log_cat$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_log_cat)
plot(roc_curve, 
     col = "#CD0BBC", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated (Empty Categories -- Can't Run)

```{r, eval = FALSE}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(919)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_cat_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "binomial", 
                                   miss_method = "cat", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_log_cat_sep$all_fold_auc
median(kfold_log_cat_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_cat_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

## Model 2: Random Forest {.tabset}
### Summary Measure Models {.tabset}
#### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 

##### Fit to Full Sample 

```{r}
# Random forest + complete-case proportion
mod_rf_prop = cc_prop_approach(outcome = "ANY_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                               data = hosp_dat, 
                               family = "binomial", 
                               use_glm = FALSE) 

# View the fitted model summary
mod_rf_prop$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_prop = mod_rf_prop$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_prop)
plot(roc_curve, 
     col = "cornflowerblue", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with complete-case proportion ALI
kfold_rf_cc_prop = kfold_validate(outcome = "ANY_ADMIT", 
                                  covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                  data = hosp_dat, 
                                  family = "binomial", 
                                  miss_method = "cc_prop", 
                                  use_glm = FALSE,
                                  folds = 5)

## View AUC from 5 folds 
kfold_rf_cc_prop$all_fold_auc
median(kfold_rf_cc_prop$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_rf_cc_prop |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 2: Counts of Unhealthy and Missing Components 

##### Fit to Full Sample 

```{r}
# Logistic regression + count of missing / unhealthy
mod_rf_num = num_miss_approach(outcome = "ANY_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                               data = hosp_dat, 
                               family = "binomial", 
                               use_glm = FALSE) 

# View the fitted model summary
mod_rf_num$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_num = mod_rf_num$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_num)
plot(roc_curve, 
     col = "cornflowerblue", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with complete-case proportion ALI
kfold_log_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "num_miss", 
                                    folds = 5)

## View AUC from 5 folds 
kfold_log_num_miss$all_fold_auc
median(kfold_log_num_miss$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_num_miss |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 3a: Best-Case Imputation

##### Fit to Full Sample 

```{r}
# Logistic regression + best-case imputation
mod_rf_best = case_approach(outcome = "ANY_ADMIT", 
                            covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                            data = hosp_dat, 
                            family = "binomial", 
                            best = TRUE, 
                            use_glm = FALSE) 

# View the fitted model summary
mod_rf_best$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_best = mod_rf_best$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_best)
plot(roc_curve, 
     col = "cornflowerblue", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with best-case imputation
kfold_rf_best = kfold_validate(outcome = "ANY_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                               data = hosp_dat, 
                               family = "binomial", 
                               miss_method = "best", 
                               use_glm = FALSE,
                               folds = 5)

## View AUC from 5 folds 
kfold_rf_best$all_fold_auc
median(kfold_rf_best$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_rf_best |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 3b: Worst-Case Imputation

##### Fit to Full Sample 

```{r}
# Logistic regression + worst-case imputation
mod_rf_worst = case_approach(outcome = "ANY_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             data = hosp_dat, 
                             family = "binomial", 
                             best = FALSE, 
                             use_glm = FALSE) 

# View the fitted model summary
mod_rf_worst$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_worst = mod_rf_worst$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_worst)
plot(roc_curve, 
     col = "cornflowerblue", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with worst-case imputation
kfold_rf_worst = kfold_validate(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial", 
                                miss_method = "worst", 
                                use_glm = FALSE,
                                folds = 5)

## View AUC from 5 folds 
kfold_rf_worst$all_fold_auc
median(kfold_rf_worst$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_rf_worst |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

### Separate Component Models {.tabset}

#### Approach 4a: Best-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# Logistic regression + best-case imputation (separate components)
mod_rf_best_sep = case_approach(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "binomial", 
                                best = TRUE, 
                                comp_sep = TRUE, 
                                use_glm = FALSE) 

# View the fitted model summary
mod_rf_best_sep$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_best_sep = mod_rf_best_sep$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_best_sep)
plot(roc_curve, 
     col = "cornflowerblue", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with best-case imputation
kfold_rf_best_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "binomial", 
                                   miss_method = "best", 
                                   comp_sep = TRUE,
                                   use_glm = FALSE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_rf_best_sep$all_fold_auc
median(kfold_rf_best_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_rf_best_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 4b: Worst-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# Random forest + worst-case imputation (separate components)
mod_rf_worst_sep = case_approach(outcome = "ANY_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                 data = hosp_dat, 
                                 family = "binomial", 
                                 best = FALSE, 
                                 comp_sep = TRUE,
                                 use_glm = FALSE) 

# View the fitted model summary
mod_rf_worst_sep$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_worst_sep = mod_rf_worst_sep$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_worst_sep)
plot(roc_curve, 
     col = "cornflowerblue", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the random forest with worst-case imputation
kfold_rf_worst_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "worst", 
                                    use_glm = FALSE,
                                    comp_sep = TRUE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_rf_worst_sep$all_fold_auc
median(kfold_rf_worst_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_rf_worst_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 5: Missingness as a Category (Separate)

```{r}
# Logistic regression + missing as a category (separate components)
mod_rf_cat = miss_cat_approach(outcome = "ANY_ADMIT",
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat,
                               family = "binomial", 
                               use_glm = FALSE)

# View the fitted model summary
mod_rf_cat$fit$variable.importance 

# Calculate predicted probabilities 
pred_prob_rf_cat = mod_rf_cat$fit$predictions[, 1]

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_rf_cat)
plot(roc_curve, 
     col = "cornflowerblue", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated (Empty Categories -- Can't Run)

```{r, eval = FALSE}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(919)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_cat_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "binomial", 
                                   miss_method = "cat", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_log_cat_sep$all_fold_auc
median(kfold_log_cat_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_log_cat_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

## Model 3: Poisson Regression {.tabset}
### Summary Measure Models {.tabset}
#### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 

##### Fit to Full Sample 

```{r}
#  poisson + complete-case proportion
mod_pois_prop = cc_prop_approach(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                data = hosp_dat, 
                                family = "poisson") 

# View the fitted model summary
mod_pois_prop$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_prop = mod_pois_prop$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_prop)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  poisson model with complete-case proportion ALI
kfold_pois_cc_prop = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "cc_prop", 
                                   folds = 5)

## View AUC from 5 folds 
kfold_pois_cc_prop$all_fold_auc
median(kfold_pois_cc_prop$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_pois_cc_prop |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```


#### Approach 2: Counts of Unhealthy and Missing Components 

##### Fit to Full Sample 

```{r}
# poisson regression + count of missing / unhealthy
mod_pois_num = num_miss_approach(outcome = "NUM_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat, 
                               family = "poisson")

# View the fitted model summary
mod_pois_num$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_num = mod_pois_num$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_num)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the poisson with complete-case proportion ALI
kfold_pois_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                    data = hosp_dat, 
                                    family = "poisson", 
                                    miss_method = "num_miss", 
                                    folds = 5)

## View AUC from 5 folds 
kfold_pois_num_miss$all_fold_auc
median(kfold_pois_num_miss$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_pois_num_miss |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 3a: Best-Case Imputation

##### Fit to Full Sample 

```{r}
# poisson regression + best-case imputation
mod_pois_best = case_approach(outcome = "NUM_ADMIT", 
                            covar = c("SEX", "AGE_AT_ENCOUNTER"),
                            data = hosp_dat, 
                            family = "poisson", 
                            best = TRUE) 

# View the fitted model summary
mod_pois_best$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_best = mod_pois_best$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_best)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  poisson with best-case imputation
kfold_pois_best = kfold_validate(outcome = "NUM_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat, 
                               family = "poisson", 
                               miss_method = "best", 
                              folds = 5)

## View AUC from 5 folds 
kfold_pois_best$all_fold_auc
median(kfold_pois_best$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_pois_best |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 3b: Worst-Case Imputation

##### Fit to Full Sample 

```{r}
# poisson regression + worst-case imputation
mod_pois_worst = case_approach(outcome = "NUM_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             data = hosp_dat, 
                             family = "poisson", 
                             best = FALSE) 

# View the fitted model summary
mod_pois_worst$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_worst = mod_pois_worst$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_worst)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the poisson with worst-case imputation
kfold_pois_worst = kfold_validate(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson", 
                                miss_method = "worst", 
                                folds = 5)

## View AUC from 5 folds 
kfold_pois_worst$all_fold_auc
median(kfold_pois_worst$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_pois_worst |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```





### Separate Component Models {.tabset}

#### Approach 4a: Best-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# poisson regression + best-case imputation (separate components)
mod_pois_best_sep = case_approach(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson", 
                                best = TRUE, 
                                comp_sep = TRUE) 

# View the fitted model summary
mod_pois_best_sep$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_best_sep = mod_pois_best_sep$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_best_sep)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the poisson with best-case imputation
kfold_pois_best_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "best", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_pois_best_sep$all_fold_auc
median(kfold_pois_best_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_pois_best_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 4b: Worst-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# poisson + worst-case imputation (separate components)
mod_pois_worst_sep = case_approach(outcome = "NUM_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                 data = hosp_dat, 
                                 family = "poisson", 
                                 best = FALSE, 
                                 comp_sep = TRUE) 

# View the fitted model summary
mod_pois_worst_sep$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_worst_sep = mod_pois_worst_sep$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_worst_sep)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the poisson with worst-case imputation
kfold_pois_worst_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    data = hosp_dat, 
                                    family = "poisson", 
                                    miss_method = "worst",
                                    comp_sep = TRUE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_pois_worst_sep$all_fold_auc
median(kfold_pois_worst_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_pois_worst_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 5: Missingness as a Category (Separate)

```{r}
# poisson + missing as a category (separate components)
mod_pois_cat = miss_cat_approach(outcome = "NUM_ADMIT",
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat,
                               family = "poisson")

# View the fitted model summary
mod_pois_cat$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_pois_cat = mod_pois_cat$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_pois_cat)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```


##### 5-Fold Cross-Validated (Empty Categories -- Can't Run)

```{r, eval = FALSE}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(919)

# 5-fold cross validation of the poisson model with best-case imputation
kfold_pois_cat_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "cat", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_pois_cat_sep$all_fold_auc
median(kfold_pois_cat_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_pois_cat_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```


## Model 4: Zero-Inflated Poisson Regression {.tabset}
### Summary Measure Models {.tabset}
#### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 

##### Fit to Full Sample 

```{r}
#  ZIP + complete-case proportion
mod_zip_prop = cc_prop_approach(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson") 

# View the fitted model summary
mod_zip_prop$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_prop = mod_zip_prop$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_prop)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  ZIP model with complete-case proportion ALI
kfold_zip_cc_prop = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "cc_prop", 
                                   folds = 5)

## View AUC from 5 folds 
kfold_zip_cc_prop$all_fold_auc
median(kfold_zip_cc_prop$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_zip_cc_prop |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 2: Counts of Unhealthy and Missing Components 

##### Fit to Full Sample 

```{r}
# ZIP regression + count of missing / unhealthy
mod_zip_num = num_miss_approach(outcome = "NUM_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                               zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat, 
                               family = "poisson")

# View the fitted model summary
mod_zip_num$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_num = mod_zip_num$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_num)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  ZIP with complete-case proportion ALI
kfold_zip_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                    zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                    data = hosp_dat, 
                                    family = "poisson", 
                                    miss_method = "num_miss", 
                                    folds = 5)

## View AUC from 5 folds 
kfold_zip_num_miss$all_fold_auc
median(kfold_zip_num_miss$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_zip_num_miss |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 3a: Best-Case Imputation

##### Fit to Full Sample 

```{r}
# ZIP regression + best-case imputation
mod_zip_best = case_approach(outcome = "NUM_ADMIT", 
                            covar = c("SEX", "AGE_AT_ENCOUNTER"),
                            zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                            data = hosp_dat, 
                            family = "poisson", 
                            best = TRUE) 

# View the fitted model summary
mod_zip_best$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_best = mod_zip_best$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_best)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the  ZIP with best-case imputation
kfold_zip_best = kfold_validate(outcome = "NUM_ADMIT", 
                               covar = c("SEX", "AGE_AT_ENCOUNTER"),
                               zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                               data = hosp_dat, 
                               family = "poisson", 
                               miss_method = "best", 
                              folds = 5)

## View AUC from 5 folds 
kfold_zip_best$all_fold_auc
median(kfold_zip_best$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_zip_best |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 3b: Worst-Case Imputation

##### Fit to Full Sample 

```{r}
# ZIP regression + worst-case imputation
mod_zip_worst = case_approach(outcome = "NUM_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                             data = hosp_dat, 
                             family = "poisson", 
                             best = FALSE) 

# View the fitted model summary
mod_zip_worst$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_worst = mod_zip_worst$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_worst)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the ZIP with worst-case imputation
kfold_zip_worst = kfold_validate(outcome = "NUM_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat, 
                                family = "poisson", 
                                miss_method = "worst", 
                                folds = 5)

## View AUC from 5 folds 
kfold_zip_worst$all_fold_auc
median(kfold_zip_worst$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_zip_worst |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

### Separate Component Models {.tabset}

#### Approach 4a: Best-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# ZIP regression + best-case imputation (separate components)
mod_zip_best_sep = case_approach(outcome = "NUM_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                 zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                 data = hosp_dat, 
                                 family = "poisson", 
                                 best = TRUE, 
                                 comp_sep = TRUE) 

# View the fitted model summary
mod_zip_best_sep$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_best_sep = mod_zip_best_sep$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_best_sep)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the ZIP with best-case imputation
kfold_zip_best_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "best", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_zip_best_sep$all_fold_auc
median(kfold_zip_best_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_zip_best_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 4b: Worst-Case Case Imputation (Separate)

##### Fit to Full Sample 

```{r}
# ZIP + worst-case imputation (separate components)
mod_zip_worst_sep = case_approach(outcome = "NUM_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                 zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                 data = hosp_dat, 
                                 family = "poisson", 
                                 best = FALSE, 
                                 comp_sep = TRUE) 

# View the fitted model summary
mod_zip_worst_sep$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_worst_sep = mod_zip_worst_sep$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_worst_sep)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```

##### 5-Fold Cross-Validated 

```{r}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the ZIP with worst-case imputation
kfold_zip_worst_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                    data = hosp_dat, 
                                    family = "poisson", 
                                    miss_method = "worst",
                                    comp_sep = TRUE,
                                    folds = 5)

## View AUC from 5 folds 
kfold_zip_worst_sep$all_fold_auc
median(kfold_zip_worst_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_zip_worst_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```

#### Approach 5: Missingness as a Category (Separate)

```{r}
# ZIP + missing as a category (separate components)
mod_zip_cat = miss_cat_approach(outcome = "NUM_ADMIT",
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                data = hosp_dat,
                                family = "poisson")

# View the fitted model summary
mod_zip_cat$fit |> 
  summary()

# Calculate predicted probabilities
pred_prob_zip_cat = mod_zip_cat$fit |> 
  predict(type = "response")

# Make the ROC curve 
roc_curve = roc(hosp_dat$ANY_ADMIT, pred_prob_zip_cat)
plot(roc_curve, 
     col = "palegreen", 
     main = "ROC Curve", 
     print.auc = TRUE)

# Calculate AUC (95% Confidence Interval)
ci.auc(roc_curve)
```


##### 5-Fold Cross-Validated (Empty Categories -- Can't Run)

```{r, eval = FALSE}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(919)

# 5-fold cross validation of the ZIP model with best-case imputation
kfold_zip_cat_sep = kfold_validate(outcome = "NUM_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   zeros = c("SEX", "AGE_AT_ENCOUNTER"),
                                   data = hosp_dat, 
                                   family = "poisson", 
                                   miss_method = "cat", 
                                   comp_sep = TRUE,
                                   folds = 5)

## View AUC from 5 folds 
kfold_zip_cat_sep$all_fold_auc
median(kfold_zip_cat_sep$all_fold_auc) ### summarized by median

## Plot individual ROC curves from 5 folds with median over top 
kfold_zip_cat_sep |> 
  kfold_roc(plot_folds = 1:5, 
            overlay_average = TRUE, 
            color_by_fold = FALSE) 
```
