---
title: "Logistic Regression Analysis (Revision)"
author: "Sarah Lotspeich"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Setup 

```{r, message = FALSE, warning = FALSE}
# Load packages
library(missALI) ## for models x missing data corrections 
library(pROC) ## for ROC curves and AUC 
library(DescTools) ## for Brier score
library(patchwork) ## to combine plots

# Read in data on hospitalizations (suppressed for privacy)
#hosp_dat = read.csv("~/Documents/missALI/data/deidentified_ali_hospitalizations.csv")
hosp_dat = read.csv("~/Documents/Allostatic_load_audits/revision_analysis_dat.csv") |> 
  ## Exclude one person with no vitals/labs before hospitalization day so all components missing
  filter(!is.na(ALI))

# Define vector of binary ALI component column names
ali_comp <- c("A1C", "ALB", "BMI", "CHOL", "CRP",
              "CREAT_C", "HCST", "TRIG", "BP_DIASTOLIC", "BP_SYSTOLIC")
```

## Exclusions 

  - Patients whose first primary care encounters were not at least 90 days before the end of the study period. 
  - For patients who were hospitalized, only visits and labs before their hospitalization (at least 1 day but no more than 3 years) were included in the averages used for ALI components. 
  - One patient (who was hospitalized) only had vitals and labs on their day of hospitalization, so they were missing all 10 components and had to be excluded. 
  - Altogether, these exclusions left us with $n=$ `r nrow(hosp_dat)` patients' data. 

# Results

```{r, echo = FALSE}
# Helper function to make ggplot ROC curves from full-sample fits 
full_sample_roc = function(roc_obj, line_col, method_title) {
  ## Create label AUC = 0.XXX
  label_auc = paste0("= ", sprintf("%.2f", round(auc(roc_obj), 2)), " (", 
                     sprintf("%.2f", round(ci.auc(roc_obj)[1], 2)), ", ", 
                     sprintf("%.2f", round(ci.auc(roc_obj)[2], 2)), ")")
  
  ## Make dataframe of ROC coordinates to plot
  #plot_roc_df = coords(roc_obj)
  
  ## Plot ROC curve(s) using ggplot2
  roc_obj |>
    ### Plot ROC coordinates
    ggroc(legacy.axes = TRUE, color = line_col) + 
    ### Add dashed line of equality for reference
    geom_abline(slope = 1,
                intercept = 0,
                linewidth = 0.5,
                linetype = "dashed") + 
    ### Final formatting
    theme_minimal(base_size = 14) +
    coord_equal() +
    annotate(geom = "text",
             x = 1,
             y = 0.07,
             hjust = 1,
             vjust = 0,
             label = "bold('AUC (95% CI)')", 
             parse = TRUE) +
    annotate(geom = "text",
             x = 1,
             y = 0,
             hjust = 1,
             vjust = 0,
             label = label_auc) +
    labs(x = "1 - Specificity",
         y = "Sensitivity", 
         title = method_title) + 
    theme(axis.title = element_text(face = "bold"), 
          title = element_text(face = "bold"))
}

# Define color scheme 
miss_meth_cols = c("#2b9d8f", "#e76f51", "#1b3c73", "#c1dbd0", 
                   "#a8c56e", "#6a4c93", "#e8b89a", "#c0404a")
```

```{r, echo = FALSE}
# Source helper functions for performance plots and metrics
source("~/Documents/missALI/analysis/calibration_functions.R")
source("~/Documents/missALI/analysis/summ_plot_predictions.R")
## For full-sample 
summ_plot_fit <- function(mod, col, method_title, model_type, missing, separate_components, B = 10000) {
  
  if (missing == "Pattern Submodels") {
    
    pred_prob <- mod |>
      predict_pattern_submod() |>
      pull(PRED)
    
  } else {
    
    pred_prob <- predict(
      mod$fit,
      type = "response"
    )
  }
  
  summ_plot_predictions(
    obs = hosp_dat$ANY_ADMIT,
    pred = pred_prob,
    col = col,
    method_title = method_title,
    model_type = model_type,
    missing = missing,
    separate_components = separate_components,
    fit_type = "Full-Sample",
    B = B,
    xlim = c(0, 0.5),
    ylim = c(0, 0.5),
    annotate = FALSE ## don't report full-sample calibration slope/intercept for logreg
  )
}
## For K-fold cross-validated
summ_plot_fit_kfold_pooled <- function(kfold_res, col, method_title, model_type, missing, separate_components, B = 10000, xlim = c(0, 1), ylim = c(0, 1)) {
  ### Pool out-of-sample predictions across all folds
  cv_dat <- do.call(
    rbind,
    lapply(
      kfold_res$all_fold_res,
      function(fold) {
        data.frame(
          obs = fold$test_roc$response,
          pred = fold$test_roc$predictor
        )
      }
    )
  )
  ### Calculate their metrics and make plots
  summ_plot_predictions(
    obs = cv_dat$obs,
    pred = cv_dat$pred,
    col = col,
    method_title = method_title,
    model_type = model_type,
    missing = missing,
    separate_components = separate_components,
    fit_type = "K-Fold",
    B = B,
    xlim = xlim,
    ylim = ylim,
    annotate = TRUE
  )
}
```

## Summary Measure Models
### Approach 1: Proportion of Non-Missing Components That Are Unhealthy 
### Fit to Full Sample 

```{r cc-prop full sample}
# Logistic regression + complete-case proportion
mod_log_prop = cc_prop_approach(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                ali = ali_comp,
                                data = hosp_dat, 
                                family = "binomial") 

## View the fitted model summary
mod_log_prop$fit |> 
  summary()

# Create plots and calculate metrics 
out = summ_plot_fit(
  mod = mod_log_prop, 
  col = miss_meth_cols[1], 
  method_title = "Complete-Case\nProportion", 
  model_type = "Logistic", 
  missing = "Complete-Case Proportion", 
  separate_components = "Summary Measure")

# Save plots as separate objects 
## ROC 
roc_log_prop = out$roc
## Calibration plot  
cal_log_prop = out$cal

# Save calibration table to separate csv 
out$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/full_sample/complete_case_proportion.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = out$df
```

### 5-Fold Cross-Validated 

```{r cc-prop k-fold}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with complete-case proportion ALI
kfold_log_cc_prop = kfold_validate(outcome = "ANY_ADMIT", 
                                   covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                   ali = ali_comp,
                                   data = hosp_dat, 
                                   family = "binomial", 
                                   miss_method = "cc_prop", 
                                   folds = 5)

# Create plots and calculate metrics 
out_kfold = summ_plot_fit_kfold_pooled(
  kfold_res = kfold_log_cc_prop, 
  col = miss_meth_cols[1], 
  method_title = "Complete-Case\nProportion", 
  model_type = "Logistic", 
  missing = "Complete-Case Proportion", 
  separate_components = "Summary Measure", 
  xlim = c(0, 0.5), 
  ylim = c(0, 0.5))

# Save plots as separate objects 
## ROC 
roc_log_prop_k = out_kfold$roc
## Calibration plot  
cal_log_prop_k = out_kfold$cal

# Save calibration table to separate csv 
out_kfold$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/cross_validated/complete_case_proportion.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out_kfold$df)
```

### Approach 2: Counts of Unhealthy and Missing Components 

### Fit to Full Sample 

```{r counts full sample}
# Logistic regression + count of missing / unhealthy
mod_log_num = num_miss_approach(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                ali = ali_comp,
                                data = hosp_dat, 
                                family = "binomial") 

# View the fitted model summary
mod_log_num$fit |> 
  summary()

# Create plots and calculate metrics 
out = summ_plot_fit(
  mod = mod_log_num, 
  col = miss_meth_cols[2], 
  method_title = "Counts of Unhealthy and\nMissing Components", 
  model_type = "Logistic", 
  missing = "Counts of Unhealthy and Missing Components", 
  separate_components = "Summary Measure")

# Save plots as separate objects 
## ROC 
roc_log_num = out$roc
## Calibration plot  
cal_log_num = out$cal

# Save calibration table to separate csv 
out$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/full_sample/counts_unhealthy_missing.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out$df)
```

### 5-Fold Cross-Validated 

```{r counts k-fold}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with complete-case proportion ALI
kfold_log_num_miss = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    ali = ali_comp,
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "num_miss", 
                                    folds = 5)

# Create plots and calculate metrics 
out_kfold = summ_plot_fit_kfold_pooled(
  kfold_res = kfold_log_num_miss, 
  col = miss_meth_cols[2], 
  method_title = "Counts of Unhealthy and\nMissing Components", 
  model_type = "Logistic", 
  missing = "Counts of Unhealthy and Missing Components",
  separate_components = "Summary Measure", 
  xlim = c(0, 0.5), 
  ylim = c(0, 0.5))

# Save plots as separate objects 
## ROC 
roc_log_num_k = out_kfold$roc
## Calibration plot  
cal_log_num_k = out_kfold$cal

# Save calibration table to separate csv 
out_kfold$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/cross_validated/counts_unhealthy_missing.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out_kfold$df)
```

### Approach 3a: Best-Case Imputation

### Fit to Full Sample 

```{r best case full sample}
# Logistic regression + best-case imputation
mod_log_best = case_approach(outcome = "ANY_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             ali = ali_comp,
                             data = hosp_dat, 
                             family = "binomial", 
                             best = TRUE) 

# View the fitted model summary
mod_log_best$fit |> 
  summary()

# Create plots and calculate metrics 
out = summ_plot_fit(
  mod = mod_log_best, 
  col = miss_meth_cols[3], 
  method_title = "Best Case\nImputation", 
  model_type = "Logistic", 
  missing = "Best Case Imputation", 
  separate_components = "Summary Measure")

# Save plots as separate objects 
## ROC 
roc_log_best = out$roc
## Calibration plot  
cal_log_best = out$cal

# Save calibration table to separate csv 
out$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/full_sample/best_case_summary.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out$df)
```

### 5-Fold Cross-Validated 

```{r best case k-fold}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_best = kfold_validate(outcome = "ANY_ADMIT", 
                                covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                ali = ali_comp,
                                data = hosp_dat, 
                                family = "binomial", 
                                miss_method = "best", 
                                folds = 5)

# Create plots and calculate metrics 
out_kfold = summ_plot_fit_kfold_pooled(
  kfold_res = kfold_log_best, 
  col = miss_meth_cols[3], 
  method_title = "Best Case\nImputation", 
  model_type = "Logistic", 
  missing = "Best Case Imputation", 
  separate_components = "Summary Measure", 
  xlim = c(0, 0.5), 
  ylim = c(0, 0.5))

# Save plots as separate objects 
## ROC 
roc_log_best_k = out_kfold$roc
## Calibration plot  
cal_log_best_k = out_kfold$cal

# Save calibration table to separate csv 
out_kfold$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/cross_validated/best_case_summary.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out_kfold$df)
```

### Approach 3b: Worst-Case Imputation

### Fit to Full Sample 

```{r worst case full sample}
# Logistic regression + worst-case imputation
mod_log_worst = case_approach(outcome = "ANY_ADMIT", 
                              covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                              ali = ali_comp,
                              data = hosp_dat, 
                              family = "binomial", 
                              best = FALSE) 

# View the fitted model summary
mod_log_worst$fit |> 
  summary()

# Create plots and calculate metrics 
out = summ_plot_fit(
  mod = mod_log_worst, 
  col = miss_meth_cols[4], 
  method_title = "Worst Case\nImputation", 
  model_type = "Logistic", 
  missing = "Worst Case Imputation", 
  separate_components = "Summary Measure")

# Save plots as separate objects 
## ROC 
roc_log_worst = out$roc
## Calibration plot  
cal_log_worst = out$cal

# Save calibration table to separate csv 
out$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/full_sample/worst_case_summary.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out$df)
```

### 5-Fold Cross-Validated 

```{r worst case k-fold}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with worst-case imputation
kfold_log_worst = kfold_validate(outcome = "ANY_ADMIT", 
                                 covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                 ali = ali_comp,
                                 data = hosp_dat, 
                                 family = "binomial", 
                                 miss_method = "worst", 
                                 folds = 5)

# Create plots and calculate metrics 
out_kfold = summ_plot_fit_kfold_pooled(
  kfold_res = kfold_log_worst, 
  col = miss_meth_cols[4], 
  method_title = "Worst Case\nImputation", 
  model_type = "Logistic", 
  missing = "Worst Case Imputation", 
  separate_components = "Summary Measure",
  xlim = c(0, 0.5), 
  ylim = c(0, 0.5))

# Save plots as separate objects 
## ROC 
roc_log_worst_k = out_kfold$roc
## Calibration plot  
cal_log_worst_k = out_kfold$cal

# Save calibration table to separate csv 
out_kfold$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/cross_validated/worst_case_summary.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out_kfold$df)
```

### ROC Curves for Approaches 1-3b 

The following plot displays the ROC curves for the four summary measure models side-by-side. 

```{r, echo = FALSE, fig.width = 16, fig.height = 10}
comb_plot = (roc_log_prop | roc_log_num | roc_log_best | roc_log_worst) / 
  (roc_log_prop_k |  roc_log_num_k | roc_log_best_k | roc_log_worst_k)
comb_plot
ggsave(filename = "~/Documents/missALI/figures/revision_all_summ_meas_roc_log.png", 
       plot = comb_plot, 
       device = "png", width = 16, height = 10, units = "in")
```

### Calibration Curves for Approaches 1-3b 

The following plot displays the ROC curves for the four summary measure models side-by-side. 

```{r, echo = FALSE, fig.width = 16, fig.height = 10}
comb_plot = (cal_log_prop | cal_log_num | cal_log_best | cal_log_worst) / (cal_log_prop_k |  cal_log_num_k | cal_log_best_k | cal_log_worst_k) #+ 
  #plot_annotation(tag_levels = "A")
comb_plot
ggsave(filename = "~/Documents/missALI/figures/revision_all_summ_meas_cal_log.png", 
       plot = comb_plot, 
       device = "png", width = 16, height = 10, units = "in")
```

### Separate Component Models

### Approach 4a: Best-Case Case Imputation (Separate)

### Fit to Full Sample 

```{r best case (sep) full sample}
# Logistic regression + best-case imputation (separate components)
mod_log_best = case_approach(outcome = "ANY_ADMIT", 
                             covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                             ali = ali_comp,
                             data = hosp_dat, 
                             family = "binomial", 
                             best = TRUE, 
                             comp_sep = TRUE) 

# View the fitted model summary
mod_log_best$fit |> 
  summary()

# Create plots and calculate metrics 
out = summ_plot_fit(
  mod = mod_log_best, 
  col = miss_meth_cols[5], 
  method_title = "Best Case\nImputation", 
  model_type = "Logistic", 
  missing = "Best Case Imputation", 
  separate_components = "Separate Components")

# Save plots as separate objects 
## ROC 
roc_log_best_sep = out$roc
## Calibration plot  
cal_log_best_sep = out$cal

# Save calibration table to separate csv 
out$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/full_sample/best_case_separate.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out$df)
```

### 5-Fold Cross-Validated 

```{r best case (sep) k-fold}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_best_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                    covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                    ali = ali_comp,
                                    data = hosp_dat, 
                                    family = "binomial", 
                                    miss_method = "best", 
                                    comp_sep = TRUE,
                                    folds = 5)

# Create plots and calculate metrics 
out_kfold = summ_plot_fit_kfold_pooled(
  kfold_res = kfold_log_best_sep, 
  col = miss_meth_cols[5], 
  method_title = "Best Case\nImputation", 
  model_type = "Logistic", 
  missing = "Best Case Imputation", 
  separate_components = "Separate Components", 
  xlim = c(0, 0.5), 
  ylim = c(0, 0.5))

# Save plots as separate objects 
## ROC 
roc_log_best_sep_k = out_kfold$roc
## Calibration plot  
cal_log_best_sep_k = out_kfold$cal

# Save calibration table to separate csv 
out_kfold$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/cross_validated/best_case_separate.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out_kfold$df)
```

### Approach 4b: Worst-Case Case Imputation (Separate)

### Fit to Full Sample 

```{r worst case (sep) full sample}
# Logistic regression + worst-case imputation (separate components)
mod_log_worst = case_approach(outcome = "ANY_ADMIT", 
                              covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                              ali = ali_comp,
                              data = hosp_dat, 
                              family = "binomial", 
                              best = FALSE, 
                              comp_sep = TRUE) 

# View the fitted model summary
mod_log_worst$fit |> 
  summary()

# Create plots and calculate metrics 
out = summ_plot_fit(
  mod = mod_log_worst, 
  col = miss_meth_cols[6], 
  method_title = "Worst Case\nImputation", 
  model_type = "Logistic", 
  missing = "Worst Case Imputation", 
  separate_components = "Separate Components")

# Save plots as separate objects 
## ROC 
roc_log_worst_sep = out$roc
## Calibration plot  
cal_log_worst_sep = out$cal

# Save calibration table to separate csv 
out$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/full_sample/worst_case_separate.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out$df)
```

### 5-Fold Cross-Validated 

```{r worst case (sep) k-fold}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_worst_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                     covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                     ali = ali_comp,
                                     data = hosp_dat, 
                                     family = "binomial", 
                                     miss_method = "worst", 
                                     comp_sep = TRUE,
                                     folds = 5)

# Create plots and calculate metrics 
out_kfold = summ_plot_fit_kfold_pooled(
  kfold_res = kfold_log_worst_sep, 
  col = miss_meth_cols[6], 
  method_title = "Worst Case\nImputation", 
  model_type = "Logistic", 
  missing = "Worst Case Imputation", 
  separate_components = "Separate Components", 
  xlim = c(0, 0.5), 
  ylim = c(0, 0.5))

# Save plots as separate objects 
## ROC 
roc_log_worst_sep_k = out_kfold$roc
## Calibration plot  
cal_log_worst_sep_k = out_kfold$cal

# Save calibration table to separate csv 
out_kfold$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/cross_validated/worst_case_separate.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out_kfold$df)
```

### Approach 5: Missingness as a Category (Separate)

### Fit to Full Sample

```{r miss cat full sample}
# Logistic regression + missing as a category (separate components)
mod_log_cat = miss_cat_approach(outcome = "ANY_ADMIT",
                                covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                ali = ali_comp,
                                data = hosp_dat,
                                family = "binomial")

# View the fitted model summary
mod_log_cat$fit |> 
  summary()

# Create plots and calculate metrics 
out = summ_plot_fit(
  mod = mod_log_cat, 
  col = miss_meth_cols[7], 
  method_title = "Missingness as\na Category", 
  model_type = "Logistic", 
  missing = "Missingness as a Category", 
  separate_components = "Separate Components")

# Save plots as separate objects 
## ROC 
roc_log_cat = out$roc
## Calibration plot  
cal_log_cat = out$cal

# Save calibration table to separate csv 
out$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/full_sample/missingness_category.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out$df)
```

### Approach 6: Pattern Submodels (Separate)

### Fit to Full Sample

```{r pattern submodels full sample}
# Logistic regression + pattern submodels (separate components)
mod_log_patsub = pattern_submod_approach(outcome = "ANY_ADMIT",
                                         covar = c("SEX", "AGE_AT_ENCOUNTER"),
                                         ali = ali_comp,
                                         data = hosp_dat,
                                         family = "binomial")

# Count how many patients had missing data patterns that needed CCS or nesting
table(mod_log_patsub$data$complete_case_submodel) ## complete-case submodel
table(mod_log_patsub$data$nested) ## nested 
# Create plots and calculate metrics 
out = summ_plot_fit(
  mod = mod_log_patsub, 
  col = miss_meth_cols[8], 
  method_title = "Pattern\nSubmodels", 
  model_type = "Logistic", 
  missing = "Pattern Submodels", 
  separate_components = "Separate Components")

# Save plots as separate objects 
## ROC 
roc_log_submod = out$roc
## Calibration plot  
cal_log_submod = out$cal

# Save calibration table to separate csv 
out$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/full_sample/pattern_submodels.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out$df)
```

### 5-Fold Cross-Validated 

```{r pattern submodels k-fold}
# Make fold assignment reproducible (same for all models + approaches)
set.seed(918)

# 5-fold cross validation of the logistic regression model with best-case imputation
kfold_log_submod_sep = kfold_validate(outcome = "ANY_ADMIT", 
                                      covar = c("SEX", "AGE_AT_ENCOUNTER"), 
                                      ali = ali_comp,
                                      data = hosp_dat, 
                                      family = "binomial", 
                                      miss_method = "patsub", 
                                      comp_sep = TRUE,
                                      folds = 5)
# Count how many patients had missing data patterns that needed CCS or nesting
kfold_test_dat = lapply(
  kfold_log_submod_sep$all_fold_res,
  function(x) x$test_data
) |>
  dplyr::bind_rows()
table(kfold_test_dat$complete_case_submodel) ## complete-case submodel
table(kfold_test_dat$nested) ## nested 

# Create plots and calculate metrics 
out_kfold = summ_plot_fit_kfold_pooled(
  kfold_res = kfold_log_submod_sep, 
  col = miss_meth_cols[8], 
  method_title = "Pattern\nSubmodels", 
  model_type = "Logistic", 
  missing = "Pattern Submodels", 
  separate_components = "Separate Components", 
  xlim = c(0, 0.5), 
  ylim = c(0, 0.5))

# Save plots as separate objects 
## ROC 
roc_log_submod_k = out_kfold$roc
## Calibration plot  
cal_log_submod_k = out_kfold$cal

# Save calibration table to separate csv 
out_kfold$cal_table |>
  write.csv("~/Documents/missALI/analysis/detailed_calibration_results/logistic_regression/cross_validated/pattern_submodels.csv", row.names = FALSE)

# Save AUC to dataframe 
save_auc = save_auc |> 
  dplyr::bind_rows(out_kfold$df)
```

```{r, echo = FALSE}
save_auc |> 
  write.csv("~/Documents/missALI/data/logistic_regression_metrics.csv", row.names = FALSE)
```

### ROC Curves for Approaches 4a-6 

The following plot displays the ROC curves for the three separate component models side-by-side. 

```{r, echo = FALSE, fig.width = 16, fig.height = 10}
design <- "
ABCD
EF#G
"
comb_plot <- (roc_log_best + roc_log_worst + roc_log_cat + roc_log_submod +
              roc_log_best_k + roc_log_worst_k + roc_log_submod_k) +
  plot_layout(design = design)
comb_plot
ggsave(filename = "~/Documents/missALI/figures/revision_all_sep_comp_roc_log.png", 
       plot = comb_plot, 
       device = "png", width = 16, height = 10, units = "in")
```

### Calibration Plots for Approaches 4a-6 

The following plot displays the calibration plots for the four separate component models side-by-side. 

```{r, echo = FALSE, fig.width = 16, fig.height = 10}
comb_plot <- (cal_log_best + cal_log_worst + cal_log_cat + cal_log_submod +
              cal_log_best_k + cal_log_worst_k + cal_log_submod_k) +
  plot_layout(design = design)
comb_plot
ggsave(filename = "~/Documents/missALI/figures/revision_all_sep_comp_cal_log.png", 
       plot = comb_plot, 
       device = "png", width = 16, height = 10, units = "in")
```